Supplement 1

### 2020-09-09 paper/supplement-1.Rmd
This should address #6

There are three broad categorisations describing why data can be 
missing: Missing Completely at Random (MCAR), Missing at Random (MAR), 
and Missing Not at Random (MNAR). These categorisations help describe 
whether the missingness occurs by chance (i.e., MCAR), due to some observed 
variable (i.e., MAR) or an unobserved variable (i.e., MNAR), with MCAR being 
the least harmful, and MAR and MNAR biased. Here, we provide an example 
of data MAR, MCAR and MNAR, relevant to football.

Data could be considered MCAR if an Australian Football data collector was taking 
a lunch break during the third quarter of a match, resulting in data not being 
recorded for this time period. Data is MCAR, because the missings are 
not systematically related to other variables.

@@

**this example still needs work** Data MNAR is when the missings are related to something unobservable. 
For example, data MNAR could arise when, if studying doping, a player 
was to remove their head and body hair, to avoid providing a hair sample for testing 
(https://www.zotero.org/google-docs/?4Ildjf). In this case, data is missing (the hair sample), 
and this information is not captured by any other variable that was collected 
(hair length was not recorded).

>>>>

One way to describe patterns of missing values is through Rubin's [@Rubin1976]
three missing data mechanisms: Missing Completely at Random (MCAR), Missing at
Random (MAR), and Missing Not at Random (MNAR). These mechanisms help describe
whether the missingness occurs by chance (MCAR), due to some observed variable
(MAR) or an unobserved variable (MNAR), with MCAR being the least harmful, and
MAR and MNAR biased. Here, we provide an example of data MAR, MCAR and MNAR,
relevant to football.

Data could be considered MCAR if an Australian Football data collector happened
to take a lunch break during the third quarter of a match, resulting in data not
being recorded for this time period. Data is MCAR, because the missings are not
systematically related to other measured variables. It would also require that this lunch break related issue didn't systematically repeat itself. That is, it is completely random.

@@

Data MNAR is when the missings are related to something unobservable or something unobserved. The previous example of data MAR could be data MNAR if the surface type was not recorded in the dataset - it would then be unobserved. Data MNAR also arises when missing values are related to the values missing. This could take place if, for example, the scales used only go up to 110Kg, and then produce missing values. This is a systematic issue - it happens each time, and means that heavier players are not recorded.

**Let me know what you think of ^^, I decided to avoid the doping example**
For example, data MNAR could arise when, if studying doping, a player 
was to remove their head and body hair, to avoid providing a hair sample for testing 
(https://www.zotero.org/google-docs/?4Ildjf). In this case, data is missing (the hair sample), 
and this information is not captured by any other variable that was collected 
(hair length was not recorded).
